Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2018-01-19 ms.tex
JM comments

\begin{abstract}
	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC. The dayside planet-to-star flux is $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside. We fit the phase variation with a range of climate maps and find they all provide reasonable fits to the data, but have large degeneracies in temperature (up to 1000 K for a given latitude/longitude). The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from 2000 K on the nightside to 3000 K on the dayside. However, the dayside spectrum has a strong feature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The emission feature is not present on the nightside, suggesting changing thermal structure with longitude. We retrieved the atmospheric composition with a 1D thermochemical equilibrium model and found the composition is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar), and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to other hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and TiO/VO.  We compare the phase curves to 3D general circulation models and find that atmospheric drag is required to explain the small hotspot offsets, but that these models overpredict the phase curve amplitude.  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find they have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
\end{abstract}

@@

Exoplanets are so distant that they are not spatially resolved, so the only way to reveal inhomogeneity in their atmospheres is to measure a phase curve. Phase curve observations consist of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet, which exposes different longitudes at each orbital phase.  The first phase curve was observed with \Spitzer\ for the hot Jupiter HD 189733b by \citep{knutson07}, followed by additional \Spitzer\ observations for about a dozen more systems \citep[cataloged in][]{parmentier17}.  The observations revealed large day-night temperature contrasts (in excess of 300 K), and eastward shifted peak brightness due to heat circulation, as predicted by 3D models \citep{showman09}.  These infrared measurements were complemented by optical phase curves from \Kepler\ that show evidence for reflected light from patchy and variable dayside clouds with a range of compositions \citep{demory13, hu15, armstrong16, parmentier16}. A \emph{spectroscopic} phase curve was observed for WASP-43b with \emph{Hubble}/Wide Field Camera 3 (\HST/WFC3) in the near-infrared, which provided the first phase-resolved measurements of an exoplanet's water abundance and thermal structure \citep{stevenson14, stevenson17}.

In this paper we present spectroscopic phase curve observations of the hot Jupiter WASP-103b, measured with \HST/WFC3 and Spitzer/IRAC. This planet is an ideal target for phase curve observations, with an orbital period of just 22 hours and an equilbrium temperature of 2500 K \citep{gillon14}.  Previous observations of WASP-103b's atmosphere revealed a blackbody-like dayside emission spectrum, with possible evidence for a $K_\mathrm{S}$-band emission feature \citep{cartier17, delrez18}. The optical transmission spectrum shows evidence for strong sodium and potassium absorption features that are consistent with expectations for a cloud-free atmosphere \citep{lendl17}.%, though other observations have shown a large optical scattering slope that is not fit well by theoretical models \citep{southworth16}.

WASP-103b is an archetype of the class of ultra-hot Jupiters, with orbital periods of about one day and dayside temperatures typically $>2000\,\mathrm{K}$. These very hot planets were initially predicted to have inverted temperature pressure profiles due to strong optical absorption by TiO/VO in the upper atmospheres \citep{hubeny03, fortney08}; however, observations of their thermal emission spectra have been puzzling. In the near-infrared, where water is the dominant absorber, some spectra show water absorption features, some show emission features, and some are consistent with blackbody models \citep{madhusudhan11, crossfield12, stevenson14b, haynes15, evans16, beatty17a, beatty17b, sheppard17, arcangeli18, mansfield18}.  A variety of explanations have been proposed for these results, including low metallicity or high carbon-to-oxygen compositions, dayside clouds, and finely tuned isothermal temperature pressure profiles. Recently, \cite{arcangeli18} showed that water dissociation on the hot dayside plays an important role in the atmospheres of these ultra-hot planets and may be responsible for some of the blackbody-like near-IR spectra. In this work, we put these results in context by investigating the global thermal structure and composition of the ultra-hot Jupiter WASP-103b.

@@

\section{Observations and Data Reduction}
\label{sec:observations}
We observed two full-orbit phase curves of WASP-103b with \HST/WFC3 and one each with \Spitzer/IRAC at 3.6 and 4.5 $\mu$m (from HST Program 14050 and Spitzer Program 11099). We also reduced two \HST/WFC3 secondary eclipse observations of WASP-103b from \HST\ Program 13660 (PI: M. Zhao).

@@

We reduced the data from both programs using a custom pipeline developed for past analyses of WFC3 data \citep[for details see][]{kreidberg14a, kreidberg14b, kreidberg15b}. Briefly, we use the optimal extraction algorithm of \cite{horne86} to extract each up-the-ramp sample (or ``stripe") separately. The stripes are then summed to create the final spectrum. For each stripe, the extraction window is 24 pixels high and centered on the stripe midpoint. We estimate the background from the median of a region of the detector that is uncontaminated by the target spectrum (rows 5-50). The typical background counts are low (10-15 photoelectrons per pixel, roughly 0.03\% of the peak counts from the target star). We note that the extracted spectrum includes flux from a nearby companion star, which is separated from WASP-103 by less than two pixels \citep[0.2";][]{wollert15}. Our extracted spectrum includes flux from this star, which we account for later in the analysis.

@@

The data were reduced with the POET pipeline \citep{stevenson12}. We performed aperture photometry with an aperture size of 2.75 pixels (chosen from a grid of apertures between 2 and 4 pixels to minimize the residual noise in the light curve fits). We masked pixels that were flagged in the bad pixel mask provided in the ancillary data for the observations. The target centroid was determined with a two-dimensional Gaussian fit.  The target remains centered near the sweet spot for the entire AOR in each observation, with a maximum drift of 0.1 pixels. We estimated and subtracted the background from an annulus with a radius of 7 to 15 pixels from the centroid. As for the \HST\ observations, the contaminating flux from the nearby star is included in the final photometry and corrected later in the light curve fits.

@@

To test that the phase-resolved spectra are robust to different approaches for fitting the data, we compared the spectra for all four of the thermal phase variation models (sinusoid, kinematic, spherical harmonics, and two temperature). We found that the choice of model does not significantly change the results.  The emission spectra are insensitive to the models because they are estimated directly from the data (after systematics have been removed). Since the systematic noise is not strongly correlated with the astrophysical signal, the systematics-divided data are nearly identical for all the models.  This point is illustrated in Figure\,\ref{fig:model_comparison} for the broadband WFC3 light curve. In most phase bins, the planet-to-star flux agrees to well within one sigma for all the models.

@@

\begin{deluxetable*}{lllllllllll}
	\tablecolumns{11}
	\tablewidth{0pt}
	\tablecaption{Phase-Resolved Emission Spectra \label{table:spectra}}
	\tablehead{
	\colhead{$\lambda$} & \colhead{Dilution} & \colhead{$\phi = 0.1$} & \colhead{$\phi = 0.2$} & \colhead{$\phi = 0.3$} & \colhead{$\phi = 0.4$} & \colhead{$\phi = 0.5$} & \colhead{$\phi = 0.6$} & \colhead{$\phi = 0.7$} & \colhead{$\phi = 0.8$} & \colhead{$\phi = 0.9$}}
		\startdata
		1.175 & 0.10 & $ 179 \pm 79 $ & $ 411 \pm 77 $ & $ 647 \pm 80 $ & $ 1143 \pm 65 $ & $ 1259 \pm 47 $ & $ 1063 \pm 64 $ & $ 710 \pm 73 $ & $ 412 \pm 78 $ & $ 177 \pm 79 $ \\ 
		1.225 & 0.11 & $ 188 \pm 76 $ & $ 398 \pm 74 $ & $ 928 \pm 77 $ & $ 1276 \pm 62 $ & $ 1448 \pm 46 $ & $ 1216 \pm 62 $ & $ 888 \pm 71 $ & $ 539 \pm 75 $ & $ 280 \pm 76 $ \\ 
		1.275 & 0.11 & $ 166 \pm 76 $ & $ 379 \pm 74 $ & $ 869 \pm 77 $ & $ 1323 \pm 62 $ & $ 1480 \pm 46 $ & $ 1282 \pm 62 $ & $ 814 \pm 71 $ & $ 515 \pm 75 $ & $ 247 \pm 76 $ \\ 
		1.325 & 0.11 & $ 266 \pm 75 $ & $ 432 \pm 73 $ & $ 904 \pm 76 $ & $ 1357 \pm 62 $ & $ 1498 \pm 45 $ & $ 1267 \pm 61 $ & $ 925 \pm 70 $ & $ 552 \pm 74 $ & $ 333 \pm 75 $ \\ 
		1.375 & 0.12 & $ 189 \pm 81 $ & $ 514 \pm 78 $ & $ 928 \pm 82 $ & $ 1376 \pm 66 $ & $ 1611 \pm 48 $ & $ 1411 \pm 65 $ & $ 954 \pm 75 $ & $ 461 \pm 79 $ & $ 292 \pm 81 $ \\ 
		1.425 & 0.13 & $ 238 \pm 79 $ & $ 532 \pm 76 $ & $ 1198 \pm 79 $ & $ 1431 \pm 64 $ & $ 1718 \pm 47 $ & $ 1511 \pm 64 $ & $ 1063 \pm 73 $ & $ 605 \pm 77 $ & $ 338 \pm 79 $ \\ 
		1.475 & 0.14 & $ 191 \pm 81 $ & $ 527 \pm 79 $ & $ 1068 \pm 82 $ & $ 1460 \pm 66 $ & $ 1667 \pm 48 $ & $ 1392 \pm 66 $ & $ 1090 \pm 75 $ & $ 580 \pm 80 $ & $ 268 \pm 81 $ \\ 
		1.525 & 0.14 & $ 143 \pm 84 $ & $ 478 \pm 81 $ & $ 1048 \pm 85 $ & $ 1429 \pm 69 $ & $ 1623 \pm 50 $ & $ 1367 \pm 68 $ & $ 943 \pm 77 $ & $ 607 \pm 82 $ & $ 291 \pm 84 $ \\ 
		1.575 & 0.15 & $ 367 \pm 88 $ & $ 761 \pm 85 $ & $ 1088 \pm 89 $ & $ 1581 \pm 72 $ & $ 1749 \pm 52 $ & $ 1503 \pm 71 $ & $ 1107 \pm 81 $ & $ 754 \pm 86 $ & $ 422 \pm 88 $ \\ 
		1.625 & 0.16 & $ 359 \pm 93 $ & $ 565 \pm 90 $ & $ 1169 \pm 94 $ & $ 1590 \pm 76 $ & $ 1843 \pm 56 $ & $ 1593 \pm 75 $ & $ 1142 \pm 86 $ & $ 542 \pm 91 $ & $ 351 \pm 93 $ \\ 
		3.6 & 0.17 & $ 1148 \pm 333 $ & $ 3633 \pm 330 $ & $ 4487 \pm 320 $ & $ 4107 \pm 314 $ & $ 4458 \pm 383 $ & $ 3495 \pm 315 $ & $ 3720 \pm 330 $ & $ 2102 \pm 331 $ & $ 1431 \pm 334 $ \\ 
		4.5 & 0.16 & $ 1586 \pm 220 $ & $ 3468 \pm 214 $ & $ 4188 \pm 190 $ & $ 5334 \pm 179 $ & $ 5686 \pm 138 $ & $ 4904 \pm 183 $ & $ 3626 \pm 214 $ & $ 2575 \pm 217 $ & $ 1057 \pm 221 $ \\ 
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
	\end{deluxetable*}

@@

\subsection{Grid-Based Retrieval}
\label{sec:retrieval}
Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based fit to the planet's atmospheric properties, similar to the grid search used in \cite{arcangeli18, mansfield18}. We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation. The stellar spectrum is scaled in intensity over the grid to model the unknown heat redistribution for the planet; i.e., a lower dayside irradiation is equivalent to more efficient heat transport to the nightside.

@@

	\item{We calculated phase-resolved spectra in ten orbital phase bins. The \HST/WFC3 spectra are consistent with  blackbody emission from the planet at all orbital phases. The best fit brightness temperatures ranges from 1920 K (phase $\phi = 0.1$) to 3010 K on the dayside. We attribute the absence of water features at WFC3 wavelengths to (1) H$_2$O dissociation on the dayside, (2) additional near-IR opacity from H-, TiO/VO and FeH, (3) a small temperature gradient at the pressure levels probed by the data.  The \Spitzer\ data are \emph{not} consistent with a blackbody: there is an infrared emission feature at phases where the substellar point is visible ($\phi = 0.2 - 0.7$), which transitions to an absorption feature on the nightside ($\phi = -0.1 - 0.1$). We attribute these features to CO absorption and changing thermal structure from the dayside to the nightside.}

>>>>

\author{Jacob Arcangeli}
\affiliation{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands}

\begin{abstract}
	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC. The dayside planet-to-star flux is $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside. We fit the phase variation with a range of climate maps and find they all provide reasonable fits to the data, but have large degeneracies in temperature (up to 1000 K for a given latitude/longitude). The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from 2000 K on the nightside to 3000 K on the dayside. However, the dayside spectrum has a strong feature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The emission feature is not present on the nightside, suggesting changes in thermal structure with longitude. We retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar), and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and TiO/VO.  We compare the phase curves to 3D general circulation models and find that atmospheric drag is required to explain the small hotspot offsets, but that these models overpredict the phase curve amplitude.  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
\end{abstract}

@@

Exoplanets are so distant that they are not spatially resolved, so the only way to reveal inhomogeneity in their atmospheres is to measure a phase curve. Phase curve observations consist of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet, which exposes different longitudes at each orbital phase.  The first phase curve of an exoplanet was observed with \Spitzer\ for the hot Jupiter HD 189733b by \cite{knutson07}, followed by additional \Spitzer\ observations for about a dozen more systems \citep[cataloged in][]{parmentier17}.  The observations revealed large day-night temperature contrasts (in excess of 300 K), and eastward shifted peak brightness due to heat circulation, as predicted by 3D models \citep{showman02}.  These infrared measurements were complemented by optical phase curves from \Kepler\ that show evidence for reflected light from patchy and variable dayside clouds with a range of compositions \citep{borucki09, demory13, hu15, armstrong16, parmentier16}. A \emph{spectroscopic} phase curve was observed for WASP-43b with \emph{Hubble}/Wide Field Camera 3 (\HST/WFC3) in the near-infrared, which provided the first phase-resolved measurements of an exoplanet's water abundance and thermal structure \citep{stevenson14, stevenson17}.

In this paper we present spectroscopic phase curve observations of the hot Jupiter WASP-103b, measured with \HST/WFC3 and Spitzer/IRAC. This planet is an ideal target for phase curve observations, with an orbital period of just 22 hours and an equilbrium temperature of 2500 K \citep{gillon14}.  Previous observations of WASP-103b's atmosphere revealed a blackbody-like dayside emission spectrum, with possible evidence for a $K_\mathrm{S}$-band emission feature \citep{cartier17, delrez18}. The optical transmission spectrum shows evidence for sodium and potassium absorption features that are consistent with expectations for a cloud-free atmosphere \citep{lendl17}.%, though other observations have shown a large optical scattering slope that is not fit well by theoretical models \citep{southworth16}.

WASP-103b is an archetype of the class of ultra-hot Jupiters, with orbital periods of about one day and dayside temperatures typically $>2000\,\mathrm{K}$. These very hot planets were initially predicted to have inverted temperature pressure profiles due to strong optical absorption by TiO/VO in the upper atmospheres \citep{hubeny03, fortney08}; however, observations of their emission spectra have been inconclusive on their thermal structure and composition. In the near-infrared, where water is the dominant absorber, some spectra show water absorption features, some show emission features, and some are consistent with blackbody models \citep{madhusudhan11, crossfield12, stevenson14b, haynes15, evans16, beatty17a, beatty17b, sheppard17, arcangeli18, mansfield18}.  A variety of explanations have been proposed for these results, including low metallicity or high carbon-to-oxygen compositions, dayside clouds, and finely tuned isothermal temperature pressure profiles. Recently, \cite{arcangeli18} showed that water dissociation and H- opacity on the hot dayside play an important role in the atmospheres of these ultra-hot planets and may be responsible for some of the blackbody-like near-IR spectra. In this work, we put these results in context by investigating the global thermal structure and composition of the ultra-hot Jupiter WASP-103b.

@@

\section{Observations and Data Reduction}
\label{sec:observations}
We observed two full-orbit phase curves of WASP-103b with \HST/WFC3 and one each with \Spitzer/IRAC at 3.6 and 4.5 $\mu$m (from HST Program 14050 and Spitzer Program 11099, PI: L. Kreidberg). We also reduced two \HST/WFC3 secondary eclipse observations of WASP-103b from \HST\ Program 13660 (PI: M. Zhao).

@@

We reduced the data from both programs using a custom pipeline developed for past analyses of WFC3 data \citep[for details see][]{kreidberg14a, kreidberg14b, kreidberg15b}. Briefly, we use the optimal extraction algorithm of \cite{horne86} to extract each up-the-ramp sample (or ``stripe") separately. The stripes are then summed to create the final spectrum. For each stripe, the extraction window is 24 pixels high and centered on the stripe midpoint. We estimate the background from the median of a region of the detector that is uncontaminated by the target spectrum (rows 5-50). The typical background counts are low (10-15 photoelectrons per pixel, roughly 0.03\% of the peak counts from the target star). We note that the extracted spectrum includes flux from a nearby companion star, which is separated from WASP-103 by less than two pixels \citep[0.2";][]{wollert15}. We account for this contamination later in the analysis.

@@

The data were reduced with the POET pipeline \citep{stevenson12}. We performed aperture photometry with an aperture size of 2.75 pixels (chosen from a grid of apertures between 2 and 4 pixels to minimize the residual noise in the light curve fits). We masked pixels that were flagged in the bad pixel mask provided in the ancillary data for the observations. The target centroid was determined with a two-dimensional Gaussian fit.  The target remains centered near the sweet spot for the entire AOR in each observation, with a maximum drift of 0.1 pixels. We estimated and subtracted the background from an annulus with a radius of 7 to 15 pixels from the centroid. The contaminating flux from the nearby star is within the same pixel as the target, so we included it in the photometry and corrected it in the light curve fits.

@@

To test that the phase-resolved spectra are robust to different approaches for fitting the data, we compared the spectra for all four of the thermal phase variation models (sinusoid, kinematic, spherical harmonics, and two temperature). We found that the choice of model does not significantly change the results.  Since the systematic noise is not strongly correlated with the astrophysical signal, the systematics-divided data are nearly identical for all the models.  This point is illustrated in Figure\,\ref{fig:model_comparison} for the broadband WFC3 light curve. For all phase bins, the estimated planet-to-star flux agrees to better than one sigma for all the models.

@@

\begin{deluxetable*}{lllllllllll}
	\tablecolumns{11}
	\tablewidth{0pt}
	\tablecaption{Phase-Resolved Emission Spectra\tablenotemark{1} \label{table:spectra}}
	\tablehead{
	\colhead{$\lambda$} & \colhead{Dilution} & \colhead{$\phi = 0.1$} & \colhead{$\phi = 0.2$} & \colhead{$\phi = 0.3$} & \colhead{$\phi = 0.4$} & \colhead{$\phi = 0.5$} & \colhead{$\phi = 0.6$} & \colhead{$\phi = 0.7$} & \colhead{$\phi = 0.8$} & \colhead{$\phi = 0.9$}}
		\startdata
		1.175 & 0.10 & $ 179 \pm 79 $ & $ 411 \pm 77 $ & $ 647 \pm 80 $ & $ 1143 \pm 65 $ & $ 1259 \pm 47 $ & $ 1063 \pm 64 $ & $ 710 \pm 73 $ & $ 412 \pm 78 $ & $ 177 \pm 79 $ \\ 
		1.225 & 0.11 & $ 188 \pm 76 $ & $ 398 \pm 74 $ & $ 928 \pm 77 $ & $ 1276 \pm 62 $ & $ 1448 \pm 46 $ & $ 1216 \pm 62 $ & $ 888 \pm 71 $ & $ 539 \pm 75 $ & $ 280 \pm 76 $ \\ 
		1.275 & 0.11 & $ 166 \pm 76 $ & $ 379 \pm 74 $ & $ 869 \pm 77 $ & $ 1323 \pm 62 $ & $ 1480 \pm 46 $ & $ 1282 \pm 62 $ & $ 814 \pm 71 $ & $ 515 \pm 75 $ & $ 247 \pm 76 $ \\ 
		1.325 & 0.11 & $ 266 \pm 75 $ & $ 432 \pm 73 $ & $ 904 \pm 76 $ & $ 1357 \pm 62 $ & $ 1498 \pm 45 $ & $ 1267 \pm 61 $ & $ 925 \pm 70 $ & $ 552 \pm 74 $ & $ 333 \pm 75 $ \\ 
		1.375 & 0.12 & $ 189 \pm 81 $ & $ 514 \pm 78 $ & $ 928 \pm 82 $ & $ 1376 \pm 66 $ & $ 1611 \pm 48 $ & $ 1411 \pm 65 $ & $ 954 \pm 75 $ & $ 461 \pm 79 $ & $ 292 \pm 81 $ \\ 
		1.425 & 0.13 & $ 238 \pm 79 $ & $ 532 \pm 76 $ & $ 1198 \pm 79 $ & $ 1431 \pm 64 $ & $ 1718 \pm 47 $ & $ 1511 \pm 64 $ & $ 1063 \pm 73 $ & $ 605 \pm 77 $ & $ 338 \pm 79 $ \\ 
		1.475 & 0.14 & $ 191 \pm 81 $ & $ 527 \pm 79 $ & $ 1068 \pm 82 $ & $ 1460 \pm 66 $ & $ 1667 \pm 48 $ & $ 1392 \pm 66 $ & $ 1090 \pm 75 $ & $ 580 \pm 80 $ & $ 268 \pm 81 $ \\ 
		1.525 & 0.14 & $ 143 \pm 84 $ & $ 478 \pm 81 $ & $ 1048 \pm 85 $ & $ 1429 \pm 69 $ & $ 1623 \pm 50 $ & $ 1367 \pm 68 $ & $ 943 \pm 77 $ & $ 607 \pm 82 $ & $ 291 \pm 84 $ \\ 
		1.575 & 0.15 & $ 367 \pm 88 $ & $ 761 \pm 85 $ & $ 1088 \pm 89 $ & $ 1581 \pm 72 $ & $ 1749 \pm 52 $ & $ 1503 \pm 71 $ & $ 1107 \pm 81 $ & $ 754 \pm 86 $ & $ 422 \pm 88 $ \\ 
		1.625 & 0.16 & $ 359 \pm 93 $ & $ 565 \pm 90 $ & $ 1169 \pm 94 $ & $ 1590 \pm 76 $ & $ 1843 \pm 56 $ & $ 1593 \pm 75 $ & $ 1142 \pm 86 $ & $ 542 \pm 91 $ & $ 351 \pm 93 $ \\ 
		3.6 & 0.17 & $ 1148 \pm 333 $ & $ 3633 \pm 330 $ & $ 4487 \pm 320 $ & $ 4107 \pm 314 $ & $ 4458 \pm 383 $ & $ 3495 \pm 315 $ & $ 3720 \pm 330 $ & $ 2102 \pm 331 $ & $ 1431 \pm 334 $ \\ 
		4.5 & 0.16 & $ 1586 \pm 220 $ & $ 3468 \pm 214 $ & $ 4188 \pm 190 $ & $ 5334 \pm 179 $ & $ 5686 \pm 138 $ & $ 4904 \pm 183 $ & $ 3626 \pm 214 $ & $ 2575 \pm 217 $ & $ 1057 \pm 221 $ \\ 
		\enddata
		\vspace{-0.8cm}
		\tablenotetext{1}{The planet-to-star flux in each phase bin $\phi$ is in units of ppm.}
	\end{deluxetable*}

@@

\subsection{Grid-Based Retrieval}
\label{sec:retrieval}
Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based fit to the planet's atmospheric properties, similar to the grid search used in \cite{arcangeli18, mansfield18}. We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation. The flux at the top of the atmosphere is scaled in intensity over the grid to model the unknown heat redistribution for the planet; i.e., a lower dayside irradiation is equivalent to more efficient heat transport to the nightside.

@@

\item{We calculated phase-resolved spectra in ten orbital phase bins. The \HST/WFC3 spectra are consistent with  blackbody emission from the planet at all orbital phases. The best fit brightness temperatures ranges from $1920\pm40$ K (phase $\phi = 0.1$) to $3010\pm10$ K on the dayside. We attribute the absence of water features at WFC3 wavelengths to (1) H$_2$O dissociation on the dayside, (2) additional near-IR opacity from H-, TiO/VO and FeH, (3) a small temperature gradient at the pressure levels probed by the data.}
\item{The \Spitzer\ data are \emph{not} consistent with a blackbody: there is an infrared emission feature at phases where the substellar point is visible ($\phi = 0.2 - 0.7$), which transitions to an absorption feature on the nightside ($\phi = -0.1 - 0.1$). We attribute these features to CO absorption and changing thermal structure from the dayside to the nightside.}
